---
title: "Final Project"
author: "Anav Singh and Prithvi Kinariwala"
date: "4/28/2020"
output: pdf_document
---
Loading Data Set and Packages
```{r}
vgsales=read.csv("C:\\Users\\Prithvi Kinariwala\\Desktop\\First_Year\\2nd Semester\\STAT 1601\\Final Project\\vgsales.csv")
library(dplyr)
library(ggplot2)
```

# Question 1: What years saw the greatest amount of game releases?
## Data Wrangling
```{r}
yeargames=vgsales
yeargames<-yeargames[!(yeargames$Year=="N/A" ),]
```

## Data Visualization
```{r}
ggplot(data = yeargames, mapping = aes(x =Year, fill= Platform)) + geom_bar()+ theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+labs(x = "Year", y="Number of Games Published",
     title = "Games Published 1980-2016")
```

```{r}
library(plotly)

g=ggplot(data = yeargames, mapping = aes(x =Year, fill= Platform)) + geom_bar()+ theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+labs(x = "Year", y="Number of Games Published",title = "Games Published 1980-2016")
ggplotly(g)
```




# Question 2: Are certain gaming platforms more violent than others?
## Data Wrangling
```{r}
violentgames=vgsales
# For-loop to classify certain genres as Violent and others as Non-violent
Violent = NULL
for(i in 1:nrow(violentgames))
{
    if(violentgames[i,5]=="Action"|violentgames[i,5]=="Fighting"|violentgames[i,5]=="Shooter" ){Violent[i]<-"Violent"}
    else{Violent[i]<-"Not Violent"}
}

# For-loop to classify platforms by platform manufacterers 
ConsoleMaker = NULL
for(i in 1:nrow(violentgames))
{
    if(violentgames[i,3]=="DS"|violentgames[i,3]=="3DS"|violentgames[i,3]=="GB"|violentgames[i,3]=="GBA"|violentgames[i,3]=="N64"|violentgames[i,3]=="NES"|violentgames[i,3]=="Wii"|violentgames[i,3]=="WiiU"){ConsoleMaker[i]<-"Nintendo"}
    else if(violentgames[i,3]=="PS"|violentgames[i,3]=="PS2"|violentgames[i,3]=="PS3"|violentgames[i,3]=="PS4"|violentgames[i,3]=="PSP"|violentgames[i,3]=="PSV"){ConsoleMaker[i]<-"Sony"}
  else if(violentgames[i,3]=="X360"|violentgames[i,3]=="XB"|violentgames[i,3]=="XOne"){ConsoleMaker[i]<-"Microsoft"}
  else{violentgames[-i]}
}

# Binding Data Together and Ommitting0 "N/A"s
violentData=cbind(violentgames,Violent,ConsoleMaker)
violentData <- na.omit(violentData)
```

## Data Visualization
Count by Platform Brand
```{r}
ggplot(data = violentData, mapping = aes(x =Platform,fill= Violent)) + 
    geom_bar()+facet_wrap(~ConsoleMaker)+
    labs(y="Number of Video Games",
         title = "Violence in Video Games by Major Platform Making Companies") +
    theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+scale_fill_manual(values = c("steelblue1","tomato2"))
```

Percent Composition by Platform Brand
```{r}
ggplot(data = violentData, mapping = aes(x =Platform,fill= Violent)) + 
     geom_bar(position="fill")+facet_wrap(~ConsoleMaker)+
     labs(y="Percent Composition",
          title = "Violence in Video Games by Platform Making Companies") +     theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+scale_fill_manual(values = c("steelblue1","tomato2"))
```

## Summarizing Data
```{r}
library(dplyr)
violence_two_way_table <- violentData %>%
  group_by(ConsoleMaker, Violent) %>% 
  summarize(count = n())
  
violence_two_way_table
```

Platform Brand Violence Proportions
```{r}
# Microsoft Platform Violent Games Proportion
1035/(1035+1267)

# Nintendo Platform Violent Games Proportion
1400/(1400+4077)

# Sony Platform Violent Games Proportion
2300/(2300+4348)
```
# Question 3: Are shooting games more popular in America than other genres?

# statistical Inference
Are mean sales of shooting games in America different from mean sales for rest of the genres in America?

Sample means by genre:
```{r}
vgsales %>%
group_by(Genre) %>%
summarise(mean_genre = mean(NA_Sales))
```

ANOVA
```{r}
anova_vg = aov(NA_Sales~Genre, vgsales)
summary(anova_vg)
```
Reject the null, we have evidence to conclude that atleast one of the population means for NA Sales across genres is different. 

Multiple Hypothesis Testing 
```{r}
anova_vg = aov(NA_Sales~Genre, vgsales)
glimpse(TukeyHSD(anova_vg))
```

Shooter vs Others (NA)

Shooter>Action
Shooter>Adventure
Shooter>Fighting
Shooter>Misc 
Shooter Platform        
Shooter>Puzzle           
Shooter>Racing           
Shooter>Role-Playing     
Simulation<Shooter     
Sports<Shooter 
Strategy<Shooter 

After an analysis of mean sales of Shooter games compared to other genres in North America, we found that the it was greater than all other genres except Platform, where the confidence interval of the difference between the means contained 0. Thus we cannot make any conclusions between the mean sales for Shooter and Platform.

Comparison with EU
```{r}
vgsales %>%
group_by(Genre) %>%
summarise(mean_genre = mean(EU_Sales))

anova_eu = aov(EU_Sales~Genre, vgsales)
summary(anova_eu)

glimpse(TukeyHSD(anova_eu))
```

Shooter vs Others (EU)

Shooter>Action
Shooter>Adventure
Shooter>Fighting
Shooter>Misc
Shooter Platform
Shooter>Puzzle
Shooter Racing
Shooter>Role-Playing
Simulation<Shooter
Sports<Shooter
Strategy<Shooter

After an analysis of mean sales of Shooter games compared to other genres in Europe, we found that the it was greater than all other genres except Platform and Racing, where the confidence interval of the difference between the means contained 0. Thus we cannot make any conclusions between the mean sales for Shooter and Platform, and Shooter and Racing.

Comparision with Japan
```{r}
vgsales %>%
group_by(Genre) %>%
summarise(mean_genre = mean(JP_Sales))

anova_jp = aov(JP_Sales~Genre, vgsales)
summary(anova_jp)

glimpse(TukeyHSD(anova_jp))
```

Shooting vs Others (Japan)

Shooter Action
Shooter Adventure
Shooter<Fighting
Shooter Misc
Shooter<Platform
Shooter<Puzzle
Shooter Racing
Shooter<Role-Playing
Simulation>Shooter
Sports Shooter
Strategy Shooter

After an analysis of mean sales of Shooter games compared to other genres in Europe, we found that the it was inconclusive for many genres, and less than many others. It shows Shooter games are not very popular in Japan.

Platform games dominated almost every early release game pre-2000s, and thus may influence sales and skew data and not give us a clear idea of current popularity statistics in the US.

Comparing Platform and Shooter, post 2000

Post-2000 data, Years = Years since 1980
```{r}
yeargames<-vgsales[!(vgsales$Year=="N/A" ),]
numeric_year = transform(yeargames, Year = as.numeric(Year))
data_2005 = numeric_year[which(numeric_year$Year > 25),]
final_data = data_2005[which(data_2005$Genre == "Platform" | data_2005$Genre == "Shooter"),]

t.test(NA_Sales ~ Genre, final_data, conf.level = 0.90)
```
We are 90% confident that the mean sales for Platform games is between 223897.87 and 13249.81 dollars lower than Shooter games.

```{r}
t.test(NA_Sales ~ Genre, final_data, alternative = "less")
```
level of significance = 10%
p-value = 3.21%

We have enough statistical evidence to conclude that mean sales for Platform games are less than Shooter games. This makes shooter games the more popular gaming genre in the USA. 


# Question 4: Is PlayStation better than Xbox?
* Comparing average sales by platform
* Comparing proportion of games released by platform

## Statistical Inferencing 
Characterize Platforms as Xbox/PlayStation
```{r}
vgsales2 = vgsales %>%
mutate(Xbox_or_Playstation = ifelse(grepl("X", Platform), "Xbox", ifelse(grepl("PS", Platform), "PlayStation", NA)))

vgsales2 = vgsales2[-(which(vgsales2$Platform == "PCFX")),]

vgsales3 = vgsales2[-(which(vgsales2$Platform == "PSP" | vgsales2$Platform == "PSV")),]

vgsales4 = na.omit(vgsales3)
```

Mean Sales
```{r}
library(dplyr)
vgsales4 %>%
group_by(Xbox_or_Playstation) %>%
summarize(mean_sales = mean(Global_Sales))

t.test(Global_Sales ~ Xbox_or_Playstation, vgsales4, conf.level = 0.95)
t.test(Global_Sales ~ Xbox_or_Playstation, vgsales4, alternative = "greater")

t.test(NA_Sales ~ Xbox_or_Playstation, vgsales4, conf.level = 0.95)
t.test(NA_Sales ~ Xbox_or_Playstation, vgsales4, alternative = "less")
```

Proportion of Video Games
```{r}
library(RColorBrewer)
library(ggplot2)
ggplot(vgsales3, aes(x = Xbox_or_Playstation)) + geom_bar(fill = brewer.pal(3, "Set1"))+labs(y="Count", x="Console" ,title = "Video Games per Platform")

prop.test(c(5022,2302), c(14971,14971), conf.level = 0.95)
prop.test(c(5022,2302), c(14971,14971), alternative = "greater")
```
We are 95% confident that the proportion of PlayStation games is between 0.1721000 and 0.1912692 higher than the proportion of Xbox games, of the total games released. 

We have enough statistical evidence to conclude that the proportion of PlayStation games is higher than the proportion of Xbox games, of the total games released.

# Question 5: Are North American or Japanese sales better at indicating how a video game does globally?

## Data Wrangling
```{r}
videogamessales=vgsales
# Labeling Games by platform brand
ConsoleCreator = NULL
for(i in 1:nrow(videogamessales))
{
    if(videogamessales[i,3]=="DS"|videogamessales[i,3]=="3DS"|videogamessales[i,3]=="GB"|videogamessales[i,3]=="GBA"|videogamessales[i,3]=="N64"|videogamessales[i,3]=="NES"|videogamessales[i,3]=="Wii"|videogamessales[i,3]=="WiiU"){ConsoleCreator[i]<-"Nintendo"}
    else if(videogamessales[i,3]=="PS"|videogamessales[i,3]=="PS2"|videogamessales[i,3]=="PS3"|videogamessales[i,3]=="PS4"|videogamessales[i,3]=="PSP"|videogamessales[i,3]=="PSV"){ConsoleCreator[i]<-"Sony"}
  else if(videogamessales[i,3]=="X360"|videogamessales[i,3]=="XB"|videogamessales[i,3]=="XOne"){ConsoleCreator[i]<-"Microsoft"}
  else{ConsoleCreator[i]<-"Other"}
}

# Binding two columns together
VideoGamesConsole=cbind(videogamessales,ConsoleCreator)
```

## Data Visualization
North American Sales vs Global Sales Without Groups
```{r}
library(ggplot2)
ggplot(data = vgsales, mapping = aes(x = NA_Sales, y =Global_Sales)) +   geom_point(alpha=0.25)+
  labs(x = "North America Sales (million)",y="Global Sales (million)",title="Global Sales by North American Sales") +geom_smooth(method = "lm", se = FALSE)
```

Japan Sales vs Global Sales Without Groups
```{r}
library(ggplot2)
ggplot(data = vgsales, mapping = aes(x = JP_Sales, y =Global_Sales)) +   geom_point(alpha=0.25)+
  labs(x = "Japan Sales (million)",y="Global Sales (million)",title="Global Sales by Japanese Sales") +geom_smooth(method = "lm", se = FALSE)
```

## Linear Regression
North America/Global Sales Linearization Model
```{r}
NAGlobalModel<-lm(Global_Sales ~ NA_Sales, data = vgsales)
summary(NAGlobalModel)
```

Japan/Global Sales Linearization Model
```{r}
JPGlobalModel<-lm(Global_Sales ~ JP_Sales, data = vgsales)
summary(JPGlobalModel)
```

North America/Global Sales Prediction
```{r}
predictData<-data.frame(NA_Sales=c(35, 45))
predict(NAGlobalModel, predictData)
```