---
title: "Video Games with R - Interactive Graphs"
author: "Prithvi Kinariwala"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Few reminders:

* This site should be refrenced after each plot is created in the main report.
* The code here can be independently run and forked. Make sure this document is knit to HTML and **not** `github_document`.
* This page requires that the `plotly` package be installed on in supplement to the packages in the main report.
* This page should be viewed as HTML on RPubs.com and not on GitHub. If you are viewing this as a rmd on GitHub, access the HTML document [here](https://rpubs.com/prithvikin/video-games-with-R-InteractiveGraphs).

Install Packages from CRAN:
```{r installation, eval=FALSE}
install.packages("ggplot2")
install.packages("dplyr")
install.packages("RColorBrewer")
install.packages("plotly")
```

Next you "activate" the packages.
```{r activatepackages, results="hide", warning=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(plotly)
```

Loading Data
```{r}
vgsales=read.csv("C:\\Users\\Prithvi Kinariwala\\Documents\\video-games-with-R\\vgsales.csv")
```

## What years saw the greatest amount of game releases?

We take the `ggplot` function from the main report and pass it through a `ggplotly` function as a parameter.
```{r interactive-timegraph}
yeargames=vgsales
yeargames<-yeargames[!(yeargames$Year=="N/A" ),]
graph1 = ggplot(data = yeargames, mapping = aes(x =Year, fill= Platform))+
  geom_bar()+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+
  labs(x = "Year", y="Number of Games Published",title = "Games Published 1980-2016")

ggplotly(graph1)
```

## Are certain gaming platforms more violent than others?
We'll do the same data wrangling and pass the resultant `ggplot` as a parameter into the `ggploty` function.

```{r}
violentgames=vgsales

# For-loop to classify certain genres as Violent and others as Non-violent
Violent = NULL
for(i in 1:nrow(violentgames))
{
    if(violentgames[i,5]=="Action"|violentgames[i,5]=="Fighting"|violentgames[i,5]=="Shooter" ){Violent[i]<-"Violent"}
    else{Violent[i]<-"Not Violent"}
}

# For-loop to classify platforms by platform manufacterers 
ConsoleMaker = NULL
for(i in 1:nrow(violentgames))
{
  if(violentgames[i,3]=="DS"|violentgames[i,3]=="3DS"|violentgames[i,3]=="GB"|violentgames[i,3]=="GBA"|violentgames[i,3]=="N64"|violentgames[i,3]=="NES"|violentgames[i,3]=="Wii"|violentgames[i,3]=="WiiU"){ConsoleMaker[i]<-"Nintendo"}
  else if(violentgames[i,3]=="PS"|violentgames[i,3]=="PS2"|violentgames[i,3]=="PS3"|violentgames[i,3]=="PS4"|violentgames[i,3]=="PSP"|violentgames[i,3]=="PSV"){ConsoleMaker[i]<-"Sony"}
  else if(violentgames[i,3]=="X360"|violentgames[i,3]=="XB"|violentgames[i,3]=="XOne"){ConsoleMaker[i]<-"Microsoft"}
  else{violentgames[-i]}
}

violentData=cbind(violentgames,Violent,ConsoleMaker)
violentData <- na.omit(violentData)
```

Interactive Stacked Bar Graph:
```{r violentgraph-counts}
graph2A = ggplot(data = violentData, mapping = aes(x =Platform,fill= Violent)) + 
  geom_bar()+facet_wrap(~ConsoleMaker)+
  labs(y="Number of Video Games",title = "Violence in Video Games by Major Platform Making Companies")+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+scale_fill_manual(values = c("steelblue1","tomato2"))

ggplotly(graph2A)
```
  
Interactive Percent Bar Graph:
```{r violentgraph-percents}
graph2B = ggplot(data = violentData, mapping = aes(x =Platform,fill= Violent))+ 
  geom_bar(position="fill")+facet_wrap(~ConsoleMaker)+
  labs(y="Percent Composition",title = "Violence in Video Games by Platform Making Companies")+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+scale_fill_manual(values = c("steelblue1","tomato2"))

ggplotly(graph2B)
```

## Is PlayStation better than Xbox?
### Is the proportion of PlayStation games greater than Xbox games?
```{r xbox_or_playstation}
vgsales2 = vgsales %>%
  mutate(Xbox_or_Playstation = ifelse(grepl("X", Platform), "Xbox", ifelse(grepl("PS", Platform), "PlayStation", NA)))

vgsales2 = vgsales2[-(which(vgsales2$Platform == "PCFX")),]
vgsales3 = vgsales2[-(which(vgsales2$Platform == "PSP" | vgsales2$Platform == "PSV")),]
vgsales4 = na.omit(vgsales3)

graph3 = ggplot(vgsales3, aes(x = Xbox_or_Playstation)) + geom_bar(fill = brewer.pal(3, "Set1"))+labs(y="Count", x="Console" ,title = "Video Games per Platform")

ggplotly(graph3)
```

## Are North American or Japanese sales better at indicating how a video game does globally?

**NA/Global Sales Scatterplot:**
```{r naglobal, warning=FALSE,message=FALSE}
graph4A = ggplot(data = vgsales, mapping = aes(x = NA_Sales, y =Global_Sales))+   
  geom_point(alpha=0.25)+
  labs(x = "North America Sales (million)",y="Global Sales (million)",title="Global Sales by North American Sales")+
  geom_smooth(method = "lm", se = FALSE)

ggplotly(graph4A)
```

**JP/Global Sales Scatterplot:**
```{r jpglobal, warning=FALSE,message=FALSE}
graph4B = ggplot(data = vgsales, mapping = aes(x = JP_Sales, y =Global_Sales))+   
  geom_point(alpha=0.25)+
  labs(x = "Japan Sales (million)",y="Global Sales (million)",title="Global Sales by Japanese Sales")+
  geom_smooth(method = "lm", se = FALSE)

ggplotly(graph4B)
```

