---
title: "Statistical and Graphical Analysis of 1980-2016 Video Games Sales"
author: "Prithvi Kinariwala"
always_allow_html: true
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Video games have become the basis of millions of childhoods across the world. Generations can attest to ubiquitous Pacman, legendary Zelda, the adventurous Mario Brothers, and brave Master Chief. From these legends have arisen corporate conglomerates, cutting-edge computational power, and a yearning fanbase.  

However, what pushes some games to the top and others to crash? What platforms are more “violent?” What region loves their sacred controllers and game cartridges the most? Would releasing a game in North America be more beneficial than releasing in Japan? Although these are questions of an over-achieving gamer, the quest was to get the bottom of some of them with R and a public dataset.  

### The Data

Video games and their respective sales from 1980-2016 were analyzed to find answers to questions regarding sales, genres, violence in video games and regional predictions. The public data set attained from [Kaggle](www. https://www.kaggle.com/gregorut/videogamesales.com) contained:  

* Rank - Ranking of overall sales
* Name - The games name 
* Platform - Platform of the games release (i.e. PC,PS4, etc.)
* Year - Year of the game's release
* Genre - Genre of the game
* Publisher - Publisher of the game
* NA_Sales - Sales in North America (in millions)
* EU_Sales - Sales in Europe (in millions)
* JP_Sales - Sales in Japan (in millions)
* Other_Sales - Sales in the rest of the world (in millions)
* Global_Sales - Total worldwide sales.

Once the data from Kaggle is downloaded, load it as a csv into RStudio. The `file.choose()` command can be used to locate the filepath for the file.
```{r}
vgsales=read.csv("C:\\Users\\Prithvi Kinariwala\\Documents\\video-games-with-R\\vgsales.csv")
```
You'll only need to import the data once, as we'll copy it within the RStudio environment for separate data wrangling. 

*Keep in mind that the data is only complete from years 1980-2016. Games marked as released past 2016 are predictions and not concrete data*

### The Tools
> "It's dangerous to go alone! Take this."    -Old Man, The Legend of Zelda

Every journey requires the right tools. For this one, the following R libraries were used. Installations are only needed once per R installation.
```{r installation, eval=FALSE}
install.packages("ggplot2")
install.packages("dplyr")
install.packages("RColorBrewer")
install.packages("plotly")
```

Next you'll need to "activate" the individual libraries. 
```{r packages, results="hide", warning=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(plotly)
```

### The Questions
Questions explored were:  

1. What years saw the greatest amount of game releases?
2. Are certain gaming platforms more violent than others?
3. Are shooting games more popular in America?
4. Is PlayStation better than Xbox?
5. Are North American or Japanese sales better at indicating how a video game does globally?


## Research Questions (and Answers!)

### What years saw the greatest amount of game releases?
Since the creation of the first rudimentary Pong game, video game development has spread across the world with demand. International developers push out games for well-known franchises as well as iconic standalones. Although it is safe to assume that more games are in circulation now than at the advent of video gaming, to what extent is this difference? When exactly were the greatest amount of video games produced and what platform was the most popular?  

The best visual would be a bar graph with the release years as the  x-axis. But first, you'll need to clean up the data by removing games with "N/A" as the year. We make a copy of the data and clean up the copy only as data wrangling differs from question to question.
```{r}
yeargames=vgsales
yeargames<-yeargames[!(yeargames$Year=="N/A" ),]
```
Next, use the `ggplot` library to create a graph.
```{r graph1A}
graph1=ggplot(data = yeargames, mapping = aes(x =Year, fill= Platform)) +
  geom_bar()+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+
  labs(x = "Year", y="Number of Games Published",title = "Games Published 1980-2016")
```
Finally, use the `plotly` library to create an interactive graph that shows statistics when rolling over data.  
*Note: If knitting to a PDF, the PDF can not support the interactive elements of the plotly library. Instead, use only the ggplot library to create a non-interactive graph.*
```{r}
ggplotly(graph1)
```


## Conclusion
> "The numbers, Mason! What do they mean?" -Jason Hudson, Call of Duty: Black Ops

## Limitations
## Works Cited
