---
title: "Statistical and Graphical Analysis of 1980-2016 Video Games Sales"
author: "Prithvi Kinariwala"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Video games have become the basis of millions of childhoods across the world. Generations can attest to ubiquitous Pacman, legendary Zelda, the adventurous Mario Brothers, and brave Master Chief. From these legends have arisen corporate conglomerates, cutting-edge computational power, and a yearning fanbase.  

However, what pushes some games to the top and others to crash? What platforms are more “violent?” What region loves their sacred controllers and game cartridges the most? Would releasing a game in North America be more beneficial than releasing in Japan? Although these are questions of an over-achieving gamer, the quest was to get the bottom of some of them with R and a public dataset.  

### The Data

Video games and their respective sales from 1980-2016 were analyzed to find answers to questions regarding sales, genres, violence in video games and regional predictions. The public data set attained from [Kaggle](www. https://www.kaggle.com/gregorut/videogamesales.com) contained:  

* Rank - Ranking of overall sales
* Name - The games name 
* Platform - Platform of the games release (i.e. PC,PS4, etc.)
* Year - Year of the game's release
* Genre - Genre of the game
* Publisher - Publisher of the game
* NA_Sales - Sales in North America (in millions)
* EU_Sales - Sales in Europe (in millions)
* JP_Sales - Sales in Japan (in millions)
* Other_Sales - Sales in the rest of the world (in millions)
* Global_Sales - Total worldwide sales.

### The Tools
> "It's dangerous to go alone! Take this."    -Old Man, The Legend of Zelda

Every journey requires the right tools. For this one, the following R libraries were used:
```{r packages, results="hide", warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(RColorBrewer)
```

## Research Questions (and Answers!)
Questions explored were:

1. What years saw the greatest amount of game releases?
2. Are certain gaming platforms more violent than others?
3. Are shooting games more popular in America?
4. Is PlayStation better than Xbox?
5. Are North American or Japanese sales better at indicating how a video game does globally?



## Conclusion
> "The numbers, Mason! What do they mean?" -Jason Hudson, Call of Duty: Black Ops

## Limitations
## Works Cited
