---
title: "Statistical and Graphical Analysis of 1980-2016 Video Games Sales"
author: "Prithvi Kinariwala & Anav Singh"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Video games have become the basis of millions of childhoods across the world. Generations can attest to ubiquitous Pacman, legendary Zelda, the adventurous Mario Brothers, and brave Master Chief. From these legends have arisen corporate conglomerates, cutting-edge computational power, and a yearning fanbase.  

However, what pushes some games to the top and others to crash? What platforms are more “violent?” What region loves their sacred controllers and game cartridges the most? Would releasing a game in North America be more beneficial than releasing in Japan? Although these are questions of an over-achieving gamer, the quest was to get the bottom of some of them with R and a public dataset.  

### The Data

Video games and their respective sales from 1980-2016 were analyzed to find answers to questions regarding sales, genres, violence in video games and regional predictions. The public data set attained from [Kaggle](www. https://www.kaggle.com/gregorut/videogamesales.com) contained:  

* Rank - Ranking of overall sales
* Name - The games name 
* Platform - Platform of the games release (i.e. PC,PS4, etc.)
* Year - Year of the game's release
* Genre - Genre of the game
* Publisher - Publisher of the game
* NA_Sales - Sales in North America (in millions)
* EU_Sales - Sales in Europe (in millions)
* JP_Sales - Sales in Japan (in millions)
* Other_Sales - Sales in the rest of the world (in millions)
* Global_Sales - Total worldwide sales.

### The Tools


```{r packages, results="hide"}
library(ggplot2)
```


## Research Questions (and Answers!)
## Conclusion
## Limitations
## Works Cited
