---
title: "Video Games with R"
always_allow_html: true
params:
  plot: NA
output: 
  github_document:
    toc: true
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Video games have become the basis of millions of childhoods across the world. Generations can attest to ubiquitous Pacman, legendary Zelda, the adventurous Mario Brothers, and brave Master Chief. From these legends have arisen corporate conglomerates, cutting-edge computational power, and a yearning fanbase.  

However, what pushes some games to the top and others to crash? What platforms are more “violent?” What region loves their sacred controllers and game cartridges the most? Would releasing a game in North America be more beneficial than releasing in Japan? Although these are questions of an over-achieving gamer, the quest is to get the bottom of some of them with R and a public dataset.  

### The Data

Video games and their respective sales from 1980-2016 were analyzed to find answers to questions regarding sales, genres, violence in video games and regional predictions. The public data set attained from [Kaggle](www. https://www.kaggle.com/gregorut/videogamesales.com) contained:  

* Rank - Ranking of overall sales
* Name - The games name 
* Platform - Platform of the games release (i.e. PC,PS4, etc.)
* Year - Year of the game's release
* Genre - Genre of the game
* Publisher - Publisher of the game
* NA_Sales - Sales in North America (in millions)
* EU_Sales - Sales in Europe (in millions)
* JP_Sales - Sales in Japan (in millions)
* Other_Sales - Sales in the rest of the world (in millions)
* Global_Sales - Total worldwide sales.

Once the data from Kaggle is downloaded, load it as a csv into RStudio. The `file.choose()` command can be used to locate the filepath for the file.
```{r}
vgsales=read.csv("C:\\Users\\Prithvi Kinariwala\\Documents\\video-games-with-R\\vgsales.csv")
```
You'll only need to import the data once, as we'll copy it within the RStudio environment for separate data wrangling. 

*Keep in mind that the data is only complete from years 1980-2016. Games marked as released past 2016 are predictions.*

### The Tools
> "It's dangerous to go alone! Take this."    -Old Man, The Legend of Zelda

Every journey requires the right tools. For this one, the following R libraries were used. Installations are only needed once per R installation.
```{r installation, eval=FALSE}
install.packages("ggplot2")
install.packages("dplyr")
install.packages("RColorBrewer")
```

Next you'll need to "activate" the individual libraries. 
```{r packages, results="hide", warning=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(RColorBrewer)
```

### The Questions
Questions explored were:  

1. What years saw the greatest amount of game releases?
2. Are certain gaming platforms more violent than others?
3. Are shooting games more popular in America?
4. Is PlayStation better than Xbox?
5. Are North American or Japanese sales better at indicating how a video game does globally?


## Research Questions (and Answers!)

### What years saw the greatest amount of game releases?
Since the creation of the first rudimentary Pong game, video game development has spread across the world with demand. International developers push out games for well-known franchises as well as iconic standalones. Although it is safe to assume that more games are in circulation now than at the advent of video gaming, to what extent is this difference? When exactly were the greatest amount of video games produced and what platform was the most popular?  

The best visual would be a bar graph with the release years as the  x-axis. But first, you'll need to clean up the data by removing games with "N/A" as the year. We make a copy of the data and clean up the copy only as data wrangling differs from question to question.
```{r}
yeargames=vgsales
yeargames<-yeargames[!(yeargames$Year=="N/A" ),]
```
Next, use the `ggplot` library to create a graph.
```{r timegraph}
ggplot(data = yeargames, mapping = aes(x =Year, fill= Platform))+
  geom_bar()+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+
  labs(x = "Year", y="Number of Games Published",title = "Games Published 1980-2016")
```
  
*An interactive version of this graph (and the steps to create it) can be found [at  the project's page on RPubs.com](https://rpubs.com/prithvikin/video-games-with-R-InteractiveGraphs)*
  
The maximum in the timeframe with given data was 2008 and 2009. This peak can be attributed to an overlap between the Sixth Console Generation (1998-2013) and Seventh Console Generation (2005-present) as well as a new demand for handheld gaming. The two years have games for both Xbox and Xbox 360, PS2 and PS3, and handhelds like the Nintendo DS and PSP.  

The following years depict a decrease in the number of games released mainly due to less game developers being able to create games to new graphics specifications of Seventh Console Generation games. Effectively put, creating games became much more intensive, with teams dedicated to specific functions, like graphics. The change between the Seventh Console Generation and Eighth Console Generation should portray the same, as seen with the drop in games in 2012-2016. In summary, as platforms become more powerful, less game studios can create games that use the full technical capacity desired by consumers. 


### Are certain gaming platforms more violent than others?

Video game platforms, like video games, have target audiences. This audience targeting is often done with the creation and release of video games exclusive to certain platforms as well as establishing developmental tools and game engines that certain genres lend themselves well to. Mario Kart's players will never throw shells on non-Nintendo platforms, Microsoft won't let Master Chief save the UNSC on a PlayStation, nor is Uncharted leaving Sony's tight grasp.

Game developers use hardware differences to create unique games for respective platforms. Nintendo’s origins have naturally evolved into platform games with Nintendo originals being the most popular. Games like Mario Kart, Mario Party, Super Smash Bros., and Wii Sports series are Nintendo’s incentives for buying it’s consoles. On the other hand, action, shooter, and fighting games like the Halo, *mostly* Call of Duty, and Grand Theft Auto series are only offered on Xbox and PlayStation consoles. Thus, the *assumptions* made by critics attribute the Xbox and PlayStation to being more violent than their Nintendo counterparts. 

*Sidenote: Although Nintendo has recently released the Switch, the company has pushed games similar to its older generations. Due to its recent release and a lack of data, the Switch was not considered for the report. Call of Duty games are released for Nintendo platforms, but certain aspects of the game are often changed.*

To tackle the question, a graphical analysis alongside population parameters would be sufficient. The action, shooter, and fighting genres were determined to be “violent" while all other genres were determined “not violent.” Counts and percentages should be analyzed to find platforms more violent than others.

Before generating the graphs, we need to add two more character vectors (columns) to the data. One for the major platform brand (Microsoft, Nintendo, Sony) and one to classify genres as violent or not. Like the first question, we create a copy of the first data set to create a unique data set after wrangling. Then, each new vector starts out empty at `NULL` before the for-loop iterates each row while determining each row.
```{r}
violentgames=vgsales

# For-loop to classify certain genres as Violent and others as Non-violent
Violent = NULL
for(i in 1:nrow(violentgames))
{
    if(violentgames[i,5]=="Action"|violentgames[i,5]=="Fighting"|violentgames[i,5]=="Shooter" ){Violent[i]<-"Violent"}
    else{Violent[i]<-"Not Violent"}
}

# For-loop to classify platforms by platform manufacterers 
ConsoleMaker = NULL
for(i in 1:nrow(violentgames))
{
  if(violentgames[i,3]=="DS"|violentgames[i,3]=="3DS"|violentgames[i,3]=="GB"|violentgames[i,3]=="GBA"|violentgames[i,3]=="N64"|violentgames[i,3]=="NES"|violentgames[i,3]=="Wii"|violentgames[i,3]=="WiiU"){ConsoleMaker[i]<-"Nintendo"}
  else if(violentgames[i,3]=="PS"|violentgames[i,3]=="PS2"|violentgames[i,3]=="PS3"|violentgames[i,3]=="PS4"|violentgames[i,3]=="PSP"|violentgames[i,3]=="PSV"){ConsoleMaker[i]<-"Sony"}
  else if(violentgames[i,3]=="X360"|violentgames[i,3]=="XB"|violentgames[i,3]=="XOne"){ConsoleMaker[i]<-"Microsoft"}
  else{violentgames[-i]}
}
```
Finally, we bind the seperate vectors with the video games data and remove any lingering "N/A"s.
```{r}
violentData=cbind(violentgames,Violent,ConsoleMaker)
violentData <- na.omit(violentData)
```
Now that we have prepared the data, we can finally start graphing! The first graph is a simple game count by platform split between violent and non-violent games. A stacked bar graph is perfect on illustrating many properties at once.
```{r violentgraph-counts}
ggplot(data = violentData, mapping = aes(x =Platform,fill= Violent)) + 
  geom_bar()+facet_wrap(~ConsoleMaker)+
  labs(y="Number of Video Games",title = "Violence in Video Games by Major Platform Making Companies")+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+scale_fill_manual(values = c("steelblue1","tomato2"))
```
  
*[An interactive version of this graph](https://rpubs.com/prithvikin/video-games-with-R-InteractiveGraphs)*  
Let's get a percent bar graph to get another insight! Mind that less-popular platforms will have their differences blown out of proportion *cough cough Wii U*.
```{r violentgraph-percents}
ggplot(data = violentData, mapping = aes(x =Platform,fill= Violent))+ 
  geom_bar(position="fill")+facet_wrap(~ConsoleMaker)+
  labs(y="Percent Composition",title = "Violence in Video Games by Platform Making Companies")+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+scale_fill_manual(values = c("steelblue1","tomato2"))
```
  
*[An interactive version of this graph](https://rpubs.com/prithvikin/video-games-with-R-InteractiveGraphs)*  
Although you should be able to see visual differences between the three major brands, the last metric to answer the question would be the population parameters themselves. We can use the `dplyr` package to create two-way table commands to give us counts that can be used to find the parameters.
```{r}
violence_two_way_table <- violentData %>%
  group_by(ConsoleMaker, Violent) %>% 
  summarize(count = n())
violence_two_way_table
```
From these numbers, we find the proportions with one of the most basic functions of R, its calculator!
```{r}
# Microsoft Platform Violent Games Proportion
1035/(1035+1267)

# Nintendo Platform Violent Games Proportion
1400/(1400+4077)

# Sony Platform Violent Games Proportion
2300/(2300+4348)
```

The figures show that the Xbox 360 has more violent games than any Nintendo platform. The same relationship is true of PlayStation 2 and PlayStation 3 over the Nintendo Platform as well. This relationship is further seen in the percent bar graphs, where WiiU’s data is skewed only due to considerably less games being created for its platform before being discontinued. After using the `dplyr` two-way-table function to create a list of violent and nonviolent counts by platform company, Microsoft had the greatest percent of violent games (44.96%) followed by Sony (34.60%) and lastly Nintendo (25.56%). The data indicates that Nintendo platforms tend to be less violent than Microsoft and Sony platforms.

Does this mean you should never buy your child a Xbox or PlayStation? **No.** My first game was Halo 2, and I turned out alright!

### Are shooting games more popular in America than other genres?

This is a big question, and can be answered from two different directions. If you remember, the data contained statistics regarding the sales of each game. Consumer demand, although a bit faulty, can be used to predict what genres of games are in demand. 

#### In the US, are mean sales of shooting games different from that of other genres? What about the world?

This question employs R’s robust statistical methods. To gain a better understanding of the data, we create a two-way table of Genres by their mean sales in North America. Data isn't being modified here, so we don't need to make a copy of it.
```{r}
vgsales %>%
group_by(Genre) %>%
summarise(mean_genre = mean(NA_Sales))
```

Right off the bat we notice that the Shooter and Platform games have greater grossing sales. The next step would be to see if Shooter sales are *significantly greater* than Platform games. For this, we use the ANOVA test on the several means to determine if one of the populations is significantly different.

```{r}
anova_vg = aov(NA_Sales~Genre, vgsales)
summary(anova_vg)
```

A p-value of 2x10^-16 is much lower than the 5% (0.05) level of significance. Thus, we reject the null and have evidence to conclude that at least one of the population means for NA Sales across genres is different.  

Performing multiple hypothesis testing using the `TukeyHSD()` function would compare all the mean sales with each other and give corresponding confidence intervals. This would allow us to better understand the ranges of average prices for the various genres.
```{r}
anova_vg = aov(NA_Sales~Genre, vgsales)
glimpse(TukeyHSD(anova_vg))
```

**Shooter vs Others (NA)**  
Shooter>Action          
Shooter>Adventure  
Shooter>Fighting  
Shooter>Misc  
Shooter Platform  
Shooter>Puzzle          
Shooter>Racing   
Shooter>Role-Playing  
Simulation<Shooter   
Sports<Shooter  
Strategy<Shooter  


After extracting those intervals that compare ‘Shooter’ games with other genres, we find that Shooter games had higher mean sales than all other genres except Platform, where the confidence interval of the difference between the means contained 0. Thus, we cannot make any conclusions between the mean sales for Shooter and Platform. However, we can say that Shooter games have a greater number of sales on average compared to the other 10 genres, in North America.
  
It could be that Shooter games are simply a generally popular genre of games across the world, and establishing a correlation between the games and violence in America could be very wrong. To test this, we used the same process of analysis but for the Europe and Japan regions.

**Comparison with EU**
```{r}
vgsales %>%
group_by(Genre) %>%
summarise(mean_genre = mean(EU_Sales))

anova_eu = aov(EU_Sales~Genre, vgsales)
summary(anova_eu)

glimpse(TukeyHSD(anova_eu))
```

**Shooter vs Others (EU)**   
Shooter>Action  
Shooter>Adventure  
Shooter>Fighting  
Shooter>Misc  
Shooter Platform  
Shooter>Puzzle  
Shooter Racing  
Shooter>Role-Playing  
Simulation<Shooter  
Sports<Shooter  
Strategy<Shooter  

In Europe, after an analysis of Shooter games compared to other genres, we found that their mean sales were greater than all other genres except Platform and Racing, where the confidence interval of the difference between the means contained 0. Thus, we cannot make any conclusions between the mean sales for Shooter and Platform, and Shooter and Racing. However, we can say that European gamers do prefer Shooting games more than most of the other genres. Furthermore, we can say that the top video game genres in Europe have a broader range.   

**Comparision with Japan**  
```{r}
vgsales %>%
group_by(Genre) %>%
summarise(mean_genre = mean(JP_Sales))

anova_jp = aov(JP_Sales~Genre, vgsales)
summary(anova_jp)

glimpse(TukeyHSD(anova_jp))
```

**Shooting vs Others (Japan)**  
Shooter Action  
Shooter Adventure  
Shooter<Fighting  
Shooter Misc  
Shooter<Platform  
Shooter<Puzzle  
Shooter Racing  
Shooter<Role-Playing  
Simulation>Shooter  
Sports Shooter  
Strategy Shooter  

In Japan, after an analysis of mean sales of Shooter games compared to other genres, we found that the Shooter game sales were inconclusive for some and less than many other genres, on average. It shows that they are not very popular in Japan, and Japan’s consumers prefer to play other genres. With this, we can conclude to some extent that Shooter games are more popular in America due to their position of highest mean sales being shared by only one other genre. 

#### Are the mean sales of Platform and Shooter games in America recently equal?

Platform games have been around since the very start of the video game industry. It was the main game genre in the market while the video game industry was smaller, and thus dominated sales before the 2000s. Thus, adding those earlier values into the sample may not paint the most recent picture between the difference in sales between Platform and Shooter games, on average, in North America. Thus, to determine a more recent measure of the current popularity between the two genres, we compare the two mean number of sales for Shooter and Platform using data after the year 2005. The year was critical in the gaming industry and marked the start of the Seventh Generation of Consoles, characterized by the launch of the Wii, Xbox 360 and the PlayStation 3.  

The data was wrangled to transform the factor column of years to a numerical column of “Years from 1980.” This allows us to filter out the years before 2005, along with removing the NAs from the Year variable that were causing problems post-transform. 
```{r}
yeargames<-vgsales[!(vgsales$Year=="N/A" ),]
numeric_year = transform(yeargames, Year = as.numeric(Year))
data_2005 = numeric_year[which(numeric_year$Year > 25),]
final_data = data_2005[which(data_2005$Genre == "Platform" | data_2005$Genre == "Shooter"),]
```

Next, we can create a test to compare two means (t test) with a set confidence level. For this example, we sent with a 90% confidence interval.

```{r}
t.test(NA_Sales ~ Genre, final_data, conf.level = 0.90)
```
We are 90% confident that the mean sales for Platform games is between 223897.87 and 13249.81 dollars lower than Shooter games.  

To finally prove that mean sales for Platform games are less than Shooter games, we can use a hypotheisis test.
```{r}
t.test(NA_Sales ~ Genre, final_data, alternative = "less")
```
level of significance = 10%  
p-value = 3.21%  

We have enough statistical evidence to conclude that mean sales for Platform games are less than Shooter games. This makes shooter games the more popular gaming genre in the USA. 

### Is PlayStation better than Xbox?

Finally, the million dollar question. Although I may be forever biased for my love for the Master Chief/Cortana duo, what do the sales say?  

To start, we add a PlayStation and Xbox column. This time around, we'll use the `ifelse` command within the `dplyr` library. Next, as we are only comparing consoles (and not handhelds) we remove all platforms not explicitly Xbox or PlayStation. "PCFX" was accidentally grouped with Xbox, but it is easier to remove it afterwards. 

```{r}
vgsales2 = vgsales %>%
  mutate(Xbox_or_Playstation = ifelse(grepl("X", Platform), "Xbox", ifelse(grepl("PS", Platform), "PlayStation", NA)))

vgsales2 = vgsales2[-(which(vgsales2$Platform == "PCFX")),]
vgsales3 = vgsales2[-(which(vgsales2$Platform == "PSP" | vgsales2$Platform == "PSV")),]
vgsales4 = na.omit(vgsales3)
```
#### Are the mean sales for PlayStation games greater than Xbox?
For this, we can use the `dplyr` package to summarize the mean global sales by Platform.
```{r}
vgsales4 %>%
  group_by(Xbox_or_Playstation) %>%
  summarize(mean_sales = mean(Global_Sales))
```

Next, we first construct a confidence interval for the difference of **Global** Xbox and Playstation sales.
```{r}
t.test(Global_Sales ~ Xbox_or_Playstation, vgsales4, conf.level = 0.95)
t.test(Global_Sales ~ Xbox_or_Playstation, vgsales4, alternative = "greater")
```
The result was a 95% confidence interval that contains 0 and corresponding p-value of 0.09381 greater than the 5% level of significance (0.05). Thus, we do not have enough statistical evidence to conclude that the mean global sales of PlayStations are greater than the mean global sales for Xbox. This means we cannot say one console is more popular, and thus better, than the other due to a higher number of global sales and general global popularity.

We can still create the same confidence interval again, but this time for North American Sales.
```{r}
t.test(NA_Sales ~ Xbox_or_Playstation, vgsales4, conf.level = 0.95)
t.test(NA_Sales ~ Xbox_or_Playstation, vgsales4, alternative = "less")
```
However, restricting the data to just NA Sales, the 95% confidence interval of the difference between PlayStation’s mean sales and Xbox’s mean sales is between -135195.26 and -60182.89. The corresponding p-value is 1.73 x 10^-7, which is much lower than the 5% level of significance. Thus, we have enough evidence to conclude that on average, the sales for PlayStation games are less than the sales for Xbox games in North America, making Xbox the more popular and better console in the region. 

#### Is the proportion of PlayStation games greater than Xbox games?
For this comparison, we use the data including the NA (other console) values in the dataset and find the proportion of Xbox and PlayStation games of the total number of games released for all consoles. 
```{r xbox_or_playstation}
ggplot(vgsales3, aes(x = Xbox_or_Playstation)) + geom_bar(fill = brewer.pal(3, "Set1"))+labs(y="Count", x="Console" ,title = "Video Games per Platform")
```
  
*[An interactive version of this graph](https://rpubs.com/prithvikin/video-games-with-R-InteractiveGraphs)*  
Using a bar graph, we can see that the number of games available for PlayStation is much higher than that for Xbox. We further this analysis by comparing the two proportions using a confidence interval with a confidence level of 95%. 
```{r}
prop.test(c(5022,2302), c(14971,14971), conf.level = 0.95)
prop.test(c(5022,2302), c(14971,14971), alternative = "greater")
```
This allows us to conclude that we are 95% confident that the proportion of PlayStation games is between 0.1721000 and 0.1912692 greater than the proportion of Xbox games. A hypothesis test further elaborates on this conclusion, giving a p-value of 2.2x10-16 which is much lower than the 5% level of significance. Hence, PlayStation users have historically had a greater number of games to choose from and the console is better than Xbox based on this comparison.

### Are North American or Japanese sales better at indicating how a video game does globally?

Amongst the markets in the data, game development occurs most in North America and Japan. Microsoft and Sony are headquartered in the United States whereas Nintendo is Japan’s largest game conglomerate. Game development studios often release games domestically to gauge demand and fix bugs before releasing to the global market. However, this prediction method only works as well as the ability of video game sales in domestic markets to estimate international sales. 

Two scatterplots with linear regression can allow us to make preliminary conclusions. North American and Japanese Sales would be the predictory variables in their respective graphs whereas Global Sales will be the response variable. The `geom_smooth` allows us to have a linear regression line drawn in the graph.  
**NA - Global Sales**
```{r na-global-sales}
ggplot(data = vgsales, mapping = aes(x = NA_Sales, y =Global_Sales))+   
  geom_point(alpha=0.25)+
  labs(x = "North America Sales (million)",y="Global Sales (million)",title="Global Sales by North American Sales")+
  geom_smooth(method = "lm", se = FALSE)
```
  
*[An interactive version of this graph](https://rpubs.com/prithvikin/video-games-with-R-InteractiveGraphs)*
```{r}
NAGlobalModel<-lm(Global_Sales ~ NA_Sales, data = vgsales)
summary(NAGlobalModel)
```
The linear regression line of North America vs Global sales had a slope of  1.791827 with an R2 value of 0.8856. This meant that for every million sales in North America, a video game, on average, made 1.791827 million total global sales. The R^2 value being sufficient enough to indicate a strong correlation between sales in North America and Global sales. The slope being close to 1.0 indicated that North America’s sales are a very good indicator of Global sales.  

**JP - Global Sales**
```{r jp-global-sales}
ggplot(data = vgsales, mapping = aes(x = JP_Sales, y =Global_Sales))+   
  geom_point(alpha=0.25)+
  labs(x = "Japan Sales (million)",y="Global Sales (million)",title="Global Sales by Japanese Sales")+
  geom_smooth(method = "lm", se = FALSE)
```
  
*[An interactive version of this graph](https://rpubs.com/prithvikin/video-games-with-R-InteractiveGraphs)*
```{r}
JPGlobalModel<-lm(Global_Sales ~ JP_Sales, data = vgsales)
summary(JPGlobalModel)
```

The linear regression line of Japan vs Global sales had a slope of  3.076039 with  R^2 value of 0.3743. This meant that for every million sales in Japan, a video game, on average, made 3.076039 million in total global sales.  

Next, we can use the `predict` function to predict how a theoretical quantity of NA or JP sales could predict Global sales.  

**North America/Global Sales Prediction**
```{r}
NApredictData<-data.frame(NA_Sales=c(35))
predict(NAGlobalModel, NApredictData)
```
Using this model, if a game got 35 million of NA Sales, its total global sales could be predicted to be 62.77716 million.

**Japan/Global Sales Prediction**
```{r}
JPpredictData<-data.frame(JP_Sales=c(35))
predict(JPGlobalModel, JPpredictData)
```
Using the same parameters as the model for the NA model, if a game earned 35 million in Japanese sales, it can be predicted that it would earn 107.9596 million total global sales.

## Limitations
The dataset didn’t contain information on games released for the year 2017 and after. Despite there not being too many major changes to the gaming industry since that year, the composition of game genres and mean sales may be different if this data was included. Furthermore, it would paint a more recent picture of the data and the conclusions. We may see a greater increase in the sales for the Shooting games genre as the years progress. Genres themselves were a bit too broad. The “Fighting” genre encompassed both the gory Mortal Kombat series as well as the child-oriented Super Smash Bros. series. Many dates were also missing. Furthermore, we may also see a greater increase in the number of Xbox games that could begin to rival that of the PlayStation in recent times. There are many more indicators that make one console better than the other, such as specifications, compatibility with new releases, user experience ratings, etc. which we did not cover and could better answer the question of comparing Xbox and PlayStation.

## Conclusion
> "The numbers, Mason! What do they mean?" -Jason Hudson, Call of Duty: Black Ops
  
Some of the key findings were that 2008 and 2009 featured the greatest number of games entering the market due to an overlap in console generations. Microsoft and Sony platforms tend to have more violent games than Nintendo platforms, due to the console brand’s target audiences. Shooting games were more popular in America compared to other regions, perhaps because of the country’s fascination with guns and their ownership along with the establishment of longtime shooter franchises. PlayStation ranked better than Xbox on our indicator of game variety, and Xbox ranked better on sales in North America. However, they both were inconclusive based on global sales. Our last finding concluded that the North American market is a better indicator of how a game released domestically would do internationally than the Japanese market. 

It has been one heck of a journey, it's only a matter of time until we embark on our next one!